Social Computing Article\thanks{This title is temporary}

### 2013-01-09 Article.tex
"refatorei" o texto

Our solution employs a fixed topology for the agent network and models cooperation through a set of {\em aggregation rules} and reasoning through a set of {\em appropriation rules}. Our aggregation rules specify how {\em Sudoku} partial solutions are copied from agent to agent, while our appropriation rules specify how agents increment these solutions with {\em Sudoku} solving techniques such as naked singles, swordfish, etc.

@@

In {\em Sudoku} strategy literature, as in chess, we find multiple techniques with iconic names. Some popular examples are the {\em naked singles} rule, the {\em naked twins} rule and the {\em swordfish} rule, studied in ~\cite{davis:mathsudoku}. These strategies intend to, given a {\em Sudoku} puzzle in a partial state of completion, generate movements to mark blank cells of the puzzle, as "{\em mark cell 1 of column 3 with value 5}". We reproduced a variety of these strategies, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of movements.

>>>>

Our solution employs a fixed topology for the agent network and models cooperation through a set of {\em aggregation rules} and reasoning through a set of {\em appropriation rules}. Our aggregation rules specify how {\em Sudoku} partial solutions are copied from agent to agent, while our appropriation rules specify how agents increment these solutions with {\em Sudoku} solving techniques such as those studied in~\cite{davis:mathsudoku}.

@@

In {\em Sudoku} strategy literature, as in chess, we find multiple techniques with iconic names. Some popular examples are the {\em naked singles} rule, the {\em hidden singles} rule and the {\em naked twins} rule, studied in ~\cite{davis:mathsudoku}. These strategies intend to, given a {\em Sudoku} puzzle in a partial state of completion, generate movements to mark blank cells of the puzzle, as {\em "mark cell 1 of column 3 with value 5"}. We reproduced a variety of these strategies, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of movements.
